---
output: github_document
---
# vaccc19de_rki_data

Collects data on the progress of COVID-19 vaccinations in Germany. Data is published by the RKI on [this page](https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Daten/Impfquotenmonitoring.html). 

The data is collected via GitHub action which uses the accompanying [{vaccc19de} R :package:](https://github.com/friep/vaccc19de). You can find the raw data (xlsx files and sheets as csvs) in `data/raw` and the time series at `data/cumulative_time_series.csv`.   

# License
## Data 
I'm currently figuring out how to license the data / whether there are any restrictions from RKI's side - I don't suspect that there are any but I haven't found any information on that yet.

## Code
Code is licensed under a MIT License. See LICENSE.md for more information. 


# Data
## `data/cumulative_time_series.csv`

Read in directly from GitHub using R:
```{r echo=TRUE, message=FALSE}
cumulative_ts <- readr::read_csv("https://raw.githubusercontent.com/friep/vaccc19de_rki_data/main/data/cumulative_time_series.csv")
```

```{r echo=FALSE, message=FALSE}
data <- readr::read_csv("data/cumulative_time_series.csv")
cnames <- colnames(data)
df <- tibble::tribble(
    ~type, ~description,
    "datetime", "datetime until which data is included ('Datenstand') as specified in the Excel file.",
    "datetime", "datetime when data was downloaded from RKI website",
    "character", "full name of Bundesland", 
    "character", "ISO 3166-2 of Bundesland",
    "double", "Cumulative total number of vaccinations in the Bundesland",
    "double", "Difference to previous day (~roughly corresponds to people vaccinated since then although delays in reporting could be the case",
    "double", "Total number of people vaccinated because of their age so far (cumulative)",
    "double", "Total number of people vaccinated because of their profession so far (cumulative)",
    "double", "Total number of people vaccinated because of medical reasons so far (cumulative)",
    "double", "Total number of people in nursing homes so far (cumulative)"
)
df$col <- cnames
knitr::kable(dplyr::select(df, col, type, description))
```


# Contribute
Contributions are very welcome. Depending on where you want to add features, please open an issue here or on [{vaccc19de} R](https://github.com/friep/vaccc19de):

- features relating to data wrangling, data cleaning of the original excel file --> [{vaccc19de} R](https://github.com/friep/vaccc19de)
- features relating to GitHub Action and daily updates of the data --> this repository

Of course, features might require changes in both repositories. Please still open issues in both repositories and then link them to each other. 

